p-adic stability in linear algebra

### 2015-01-05 examples/stability.tex
Changed abstract, sage file for experimenting with characteristic polynomials

\title{About p-adic stability in linear algebra}

@@

\begin{abstract}
Based on the framework of ``differential precision'' developed in a
previous work by the same authors, we study 
the $p$-adic stability of standard operations on matrices and vector 
spaces. In particular, we highlight that lattice-based methods can be
quite profitable in many cases (\emph{e.g.} matrix multiplication). We 
underpin this observation by numerous numerical evidences.
\end{abstract}

>>>>

\title{p-adic stability in linear algebra}

@@

\begin{abstract}
Using the differential precision methods developed previously by the same authors,
we study the $p$-adic stability of standard operations on matrices and vector 
spaces. We demonstrate that lattice-based methods surpass naive methods in many
applications, such as matrix multiplication and sums and intersections of subspaces.
We also analyze determinants and characteristic polynomials using these differential methods.
We supplement these observations with numerical experiments.
\end{abstract}
